Puyuma: Linux-based RTOS experimental platform for constructing self-driving miniature vehicles

### 2017-04-20 cthpc-2017/paper.tex
Add conclusion

Most system use pulse width modulation (PWM) to simulate the analog signal for smooth motor controlling. PWM signal was often generated by hardware, known as hardware PWM. On the contrary, using general-purpose input/output (GPIO) to simulate the PWM signal, known as software PWM.

We built the software PWM kernel module with Xenomai real-time API, named after KsoftPWM. With the real-time application, it ensures the precision of KsoftPWM signal generation. Furthermore, the KsoftPWM was built in kernel space to eliminate the system call overhead from user space.

@@

For ease of calculation, apply extrinsic matrix that transforms the image from car's view to the road upper view  to the segments, causing a straightforward coordinate parallel to lane.
Moreover, The camera on the car is mounted in a distance from the origin. In order to know the real lateral displacement of the car, a transformation is need for converting camera frame into car frame.

@@

	The pose controller is a cascaded PID controller.The $\phi$ controller is a low level controller for lane orientation stabilizing, and d controller fix the lateral displacement by changing the setpoint of $\phi$ controller to turn left or right.
The wheel control signal (PWM) is simply the throttle value plus the correction value:

@@

Based on the works mentioned above, this section we present some experimental results that quantify the performance of the system real time ability on stressed environment. In addition, we measure three kinds of tasks which were executed in user space, kernel space and irq task, respectively. We also compare performance of KsoftPWM, non-real-time PWM kernel module (nRTPKM) and WiringPi, the most famous library for GPIO controlling on Raspberry Pi.

	The measurement were obtained using Raspberry Pi 3 with 1.2GHz ARM Cortex-A53 CPU on a Broadcom bcm2709 chip, and the system load was generated by Linux Test Project (LTP). Linux Test Project provides a collection of tools for validating the reliability, robustness, and stability of Linux. Unit of latency is microsecond in all measurement.

\begin{figure}	
	\centering
	\includegraphics[width=2in]{img/stock_kernel.png}
	\caption{Stock Kernel Performance}
	\label{fig:stock_kernel_perf}
\end{figure}

@@

Real-time performance is measured by stressing the system with LTP and applying cyclictest. We use LTP $-i$ and $-c$ flags to present the background CPU load with multiple processes and accessing on IO bus. Figure \ref{fig:stock_kernel_perf} shows the latency distribution in stock kernel. In contrast, measurement in Xenomai environment, shown in figure \ref{fig:xeno_perf}, obviously, Xenomai provides much better real-time performance. The customized kernel present better real-time ability in the user and kernel space, shown in figure \ref{fig:xeno_perf_modify}. Table \ref{xeno_compare} records the maximum latency for Xenomai in both original and customized kernel.

@@

The KsoftPWM performs better real-time ability than the others, shown in figure \ref{fig:ksoftpwm_perf}. The WiringPi real-time ability is similar to nRTPKM, since both of them are not in Xenomai environment and perform like the stock kernel. The difference of minimum latency between WiringPi and nRTPKM was caused by different implementation. nRTPKM uses sleep function to simulate the PWM signal, and WiringPi uses busy-waiting delay function to implement which may cause higher system load.

@@

>>>>

Most system use pulse width modulation (PWM) to simulate the analog signal for smooth motor controlling. PWM signals are often generated by certain hardware. On the contrary, using general-purpose input/output (GPIO) to simulate PWM signals is known as software PWM. We implement the later as a Xenomai kernel-mode real-time task to ensure the precision of PWM signal generation, named after KsoftPWM, for closed-loop control system, benefiting from the limination of system call overhead and potential locks.

@@

To reduce computation efforts, we apply extrinsic matrix that transforms the image from car's view to the road upper view to the segments, causing a straightforward coordinate parallel to lane. Moreover, the car camera is mounted in a distance from the origin. In order to know the real lateral displacement of the car, a transformation is needed for converting camera frame into car frame.

@@

The pose controller is a cascaded PID controller. The $\phi$ controller is a low level controller for lane orientation stabilizing, and d controller fix the lateral displacement by changing the setpoint of $\phi$ controller to turn left or right.
The wheel control signal generating PWM is simply the throttle value plus the correction value:

@@

We executed tasks in user space, kernel space and irq task respectively, to evaluate real-time capability. We also compare performance among KsoftPWM, non-real-time PWM kernel module (nRTPKM) and WiringPi \cite{WiringPi}, the most famous library for GPIO controlling on Raspberry Pi 3 (Broadcom bcm2709 SoC, 1.2GHz ARM Cortex-A53 CPU). The background system load was generated by Linux Test Project (LTP), which provides a collection of tools for validating the reliability, robustness, and stability of Linux. Unit of latency is microsecond in all measurement.

@@

Real-time performance is measured by stressing the system with LTP and applying cyclictest. We use LTP $-i$ and $-c$ flags to present the background CPU load with multiple processes and accessing on IO bus. Our customized Linux kernel brings better real-time ability in both user and kernel space, shown in figure \ref{fig:xeno_perf_modify}. Table \ref{xeno_compare} records the maximum latency for Xenomai.

@@

The KsoftPWM outperforms in better real-time ability, shown in figure \ref{fig:ksoftpwm_perf}. The latency distribution of WiringPi is similar to nRTPKM, since both of them are just normal Linux userspace tasks rather than hard real-time one. The difference of minimum latency between WiringPi and nRTPKM was caused by different implementation. nRTPKM uses sleep function to simulate the PWM signals while WiringPi uses busy-waiting delay which may cause higher system load.

@@

\section{Conclusion}

This paper presents the hardware and software architecture of a self-driving miniature vehicle based entirely on cost-efficient components, that implies strategic values for the long term evaluation. RTOS should be very efficient in terms of resource usage and runtime. The context switching performance is important because the number of sensors can be high and we need to read data from different sensors continuously in real-time. Linux with real-time extension  fulfills all these criteria e.g., performance, reusability, changeability, and maintainability, whichhave significant value from the software engineer's perspective. Puyuma is released as an open source project as well as ROS, allowing further collaboration on algorithms and system integration.
